NHF1_FeatureRelativeFigureGeneration

### 2023-07-27 R/NHF1_FeatureRelativeDataGeneration.Rmd
Updated feature analysis notebooks
New analysis based on changes to underlying pipeline. (Still in flux)

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_POSITION,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_THREE_PRIME_CUT_SITE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_FIVE_PRIME_CUT_SITE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

      fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_FIVE_PRIME_CUT_SITE_DISTANCE,
                                      strandAlign = TRUE),
             sep = '\t', file = generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
        additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related")
      ))

    }
  }
}

>>>>

      for (bool in c(TRUE, FALSE)) {

        if (bool) {strandInfoText = "_strand_aligned"} else {strandInfoText = ""}

        fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_POSITION,
                                        strandAlign = bool),
               sep = '\t', na = "NA", file = generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related",strandInfoText)
        ))

        fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_THREE_PRIME_CUT_SITE,
                                        strandAlign = bool),
               sep = '\t', na = "NA", file = generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = THREE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related",strandInfoText)
        ))

        fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = FEATURE_RELATIVE_FIVE_PRIME_CUT_SITE,
                                        strandAlign = bool),
               sep = '\t', na = "NA", file = generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeCutSiteCounts, ".tsv", strandPolarity = FIVE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related",strandInfoText)
        ))

        fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                        strandAlign = bool),
               sep = '\t', na = "NA", file = generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related",strandInfoText)
        ))

        fwrite(getFeatureRelativeCounts(cpdFeatureRelativeData[[i]][[j]][[k]], dataType = MEAN_FIVE_PRIME_CUT_SITE_DISTANCE,
                                        strandAlign = bool),
               sep = '\t', na = "NA", file = generateFilePath(
          featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
          cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
          timepoint = names(cpdFeatureRelativeData)[i], includedMismatches = names(cpdFeatureRelativeData[[i]])[j],
          additionalInformation = paste0(names(cpdFeatureRelativeData[[i]][[j]])[k],"_related",strandInfoText)
        ))

      }
    }
  }
}

### 2023-07-27 R/NHF1_FeatureRelativeFigureGeneration.Rmd
Updated feature analysis notebooks
New analysis based on changes to underlying pipeline. (Still in flux)

      featureRelativePositionData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related")
      ))

      meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related")
      ))

      meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related")
      ))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanThreePrimeCutSiteDistanceData,
                                THREE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanFivePrimeCutSiteDistanceData,
                                FIVE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

@@

      featureRelativePositionData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap,"_related")
      ))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanThreePrimeCutSiteDistanceData,
                                THREE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION, meanFivePrimeCutSiteDistanceData,
                                FIVE_PRIME, title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

>>>>

      featureRelativePositionData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related_strand_aligned")
      ))

      meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related_strand_aligned")
      ))

      meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(tfbs,"_related_strand_aligned")
      ))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
                                countsPlotColor = "black", countsMirrorColor = "gold2",
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

@@

      featureRelativePositionData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativePositionCounts, ".tsv",
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap,"_related_strand_aligned")
      ))

      meanThreePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = THREE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap,"_related_strand_aligned")
      ))

      meanFivePrimeCutSiteDistanceData = fread(generateFilePath(
        featureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv", strandPolarity = FIVE_PRIME,
        cellType = cellType, lesion = "CPD", repitition = "all_reps", filtering = filtering,
        timepoint = CPDTimepoint, includedMismatches = mismatchType,
        additionalInformation = paste0(nucMap,"_related_strand_aligned")
      ))

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))
